### 2019-06-24 Memoria/Chapters/Introduction.tex
Terminado capitulo 3

One of the most basic and primitive abilities that human beings are endowed with is that of grouping similar objects to produce a classification that is useful to them. For example, they should have been able to realize which objects were edible, which were poisonous, and which would try to kill them.

@@

Just as classification is a basic skill for people in their daily lives, it is also essential in most branches of science. In biology, for example, the classification of different types of organisms has been the subject of study since the beginning of their existence. Aristotle built an elaborated animal classification system that divided all creatures into two groups, those with red blood and those without. Later he proposed a subdivision that classified them according to the way in which new individuals came into the world, either alive, by means of eggs, chrysalis, etc.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[scale=0.35]{gfx/Intro/HR_diagram} 
	\caption[Hertzsprung-Russell starts classification diagram]{Hertzsprung-Russell starts classification diagram}\label{fig:intro_HRdiagram}
\end{figure}

\section{The learning task}

@@

One of the major differences between human learning and machine learning, and we must admit that in this the machines again lead us, is the way in which knowledge is transferred. In machines it is enough to copy and paste, that is to say, once a program performs correctly the task for which it has been designed in a computer, it performs it in all of them. Just copy and paste. In humans this is not the case, we cannot extract knowledge from one brain and insert it into another, we don't even know how it is encoded! We humans must use our inefficient input-output devices to transmit knowledge. The following quote, which well reflects the reality of automatic learning, is more than thirty years old, yet still valid:

>>>>

One of the most basic and primitive abilities that human beings are endowed with is being able to group similar objects to produce a classification that is useful to them. For example, they should have been able to realize which objects were edible, which were poisonous, and which would try to kill them.

@@

Just as classification is a basic skill for people in their daily lives, it is also essential in most branches of science. In biology, for example, the classification of different types of organisms has been the subject of study since the beginning of its existence. Aristotle built an elaborated animal classification system, dividing all creatures into two groups: red-blooded and not red-blooded. Later he proposed a subdivision that classified them according to the way in which new individuals came into the world, either alive, by means of eggs, chrysalis, etc.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[scale=0.35]{gfx/Intro/HR_diagram} 
	\caption[Hertzsprung-Russell stars classification diagram.]{Hertzsprung-Russell stars classification diagram.}\label{fig:intro_HRdiagram}
\end{figure}

\section{The Learning Task}

@@

One of the major differences between human learning and machine learning, and we must admit that to this respect machines again lead us, is the way in which knowledge is transferred. In machines it is enough to copy and paste, that is to say, once a program performs correctly the task for which it has been designed in a computer, it performs it in all of them. Just copy and paste. In humans this is not the case, we cannot extract knowledge from one brain and insert it into another, we don't even know how it is encoded! We humans must use our inefficient input-output devices to transmit knowledge. The following quote, which well reflects the reality of automatic learning, is more than thirty years old, yet still valid:
